Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter

### 2022-02-19 paper.tex
updates

\author[jbnu]{Junlee~Kim\corref{cor1}}
\ead{junlee.kim@cern.ch}
\cortext[cor1]{Corresponding author. Tel.: +82-xxxxxxxxx.}
\author[jbnu]{Eun-Joo~Kim\corref{cor2}}
\ead{ejkim@jbnu.ac.kr}

\author[korea]{Young~Jun~Kim}
\author[korea]{Jung~Keun~Ahn}

\cortext[cor2]{Corresponding author. Tel.: +82-xxxxxxxxx.}
\author[kek]{Gei~Youb~Lim}

@@

\begin{abstract}
We report simulation results on the angular resolution of electromagnetic (EM) sampling calorimeters with photons being in the range of 100~MeV to 2~GeV. A simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick Pb plate and a 5-mm-thick plastic scintillator plate. The scintillator plates are alternatively segmented in horizontal and vertical strips. In this study, we obtained energy deposit in individual strips using Geant4 simulations and reconstructed incident photon angles using a XGBoost model with boosted decision trees. Angular resolutions are studied in terms of the strip width. The 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$. Incident photon directions can be well reconstructed in the front part (5$X_{0}$) of the EM calorimeter. The angular resolution is almost constant for small angles less than 30$^{\circ}$, and varies significantly with the incident photon energy. The
energy dependence can be expressed as $\sigma_{\theta}=$~xxx~$\oplus$~yyy~$/\sqrt{E_{\gamma}}$.

@@

\begin{figure}[!hbt]
\includegraphics[width=0.6\textwidth]{figures/FullLayer_3.jpeg}
\caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of a Pb plate and a segmented scintillator plate in 35 strips. Each scintillator plate is oriented alternatively in horizontal and vertical directions. See text for details. }
\label{fig:det_conf}
\end{figure}

@@

\begin{figure}[!hbt]
\includegraphics[width=0.7\textwidth]{figures/GG_fit.jpg}
\caption{ Reconstructed polar angle distribution for 1-GeV photons generated at $\theta=$~10$^{\circ}$. The distribution is fitted with the Gaussian and the Generalized Gaussian function. The later gives a better result.}
\label{fig:angle_10degree}
\end{figure}

@@

\begin{table}[hbt!]
\centering
\caption{Hyperparameters of the $\XGB$}
\begin{tabular}{cccc}
\hline 
Parameter & Function & Default value & Used value \\ \hline 
N\_estimators & The number of decision trees & N.A. & 300 \\  
Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
Subsample & Fraction of total data used for a single decision & 1 & 0.8 \\ 
Learning rate & Step length for calculation & 0.3 & 0.02 \\ 
Gamma & Requirement on minimum loss function & 0 & 0 \\ 
\hline
\end{tabular}
\label{tab:XgbPar}
\end{table}

\begin{figure}[!hbt]
\includegraphics[width=0.58\textwidth]{figures/res_width.jpg}
\caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
\label{fig:angle_reco_width}
\end{figure}

@@

\begin{figure}[!hbt]
\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
\includegraphics[width=0.48\textwidth]{figures/res_Nlayer.jpg}
}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
\includegraphics[width=0.48\textwidth]{figures/resol_Nlayer.jpg}
}
\caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$. Red histogram represents the polar angle distribution by requiring $E_{\rm{tot}}>$~10~MeV. (b) Angular resolution as a function of radiation length ($X_{0}$).}
\label{fig:angle_reco_layer}
\end{figure}

@@

\begin{figure}[!hbt]
\includegraphics[width=0.6\textwidth]{figures/layer-event.jpg}
\caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths using the first 24 layers or the full layers. }
\label{fig:multi-parameter}
\end{figure}

>>>>

\author[jbnu]{Junlee~Kim}
\ead{junlee.kim@cern.ch}
%\cortext[cor1]{Corresponding author. Tel.: +82-xxxxxxxxx.}

\author[jbnu]{Eun-Joo~Kim\corref{cor1}}
\ead{ejkim@jbnu.ac.kr}
\cortext[cor1]{Corresponding author. Tel.: +82-10-4581-5649.}

\author[korea]{Young~Jun~Kim}
\author[korea]{Jung~Keun~Ahn}
\author[kek]{Gei~Youb~Lim}

@@

\begin{abstract}
We report simulation results on the angular resolution of electromagnetic (EM) sampling calorimeters with photons being in the range of 100~MeV to 2~GeV. A simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick Pb plate and a 5-mm-thick plastic scintillator plate. The scintillator plates are alternatively segmented in horizontal and vertical strips. In this study, we obtained energy deposit in individual strips using Geant4 simulations and reconstructed incident photon angles using a XGBoost model with boosted decision trees. Angular resolutions are studied in terms of the strip width. The 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$. Incident photon directions can be well reconstructed in the front part (5$X_{0}$) of the EM calorimeter still possessing the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$. The angular resolution is almost constant for small angles less than 30$^{\circ}$, and varies significantly with the incident photon energy. The
energy dependence can be expressed as $\sigma_{\theta}=$~1.21~$\oplus$~0.45~$/\sqrt{E_{\gamma}}$.

@@

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.6\textwidth]{figures/FullLayer_3.jpeg}
\caption{ Schematic of the sampling calorimeter model consisting of 105 alternating layers of a Pb plate and a segmented scintillator plate in 35 strips. Each scintillator plate is oriented alternatively in horizontal and vertical directions. See text for details. }
\label{fig:det_conf}
\end{figure}

@@

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.7\textwidth]{figures/GG_fit.jpg}
\caption{ Reconstructed polar angle distribution for 1-GeV photons generated at $\theta=$~10$^{\circ}$. The distribution is fitted with the Gaussian and the Generalized Gaussian function. The later gives a better result.}
\label{fig:angle_10degree}
\end{figure}

@@

\begin{table}[hbt!]{\small
\centering
\caption{Hyperparameters of the $\XGB$}
\begin{tabular}{cccc}
\hline 
Parameter & Function & Default value & Used value \\ \hline 
N\_estimators & The number of decision trees & N.A. & 300 \\  
Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
Subsample & Fraction of total data used for a single decision & 1 & 0.8 \\ 
Learning rate & Step length for calculation & 0.3 & 0.02 \\ 
Gamma & Requirement on minimum loss function & 0 & 0 \\ 
\hline
\end{tabular}
\label{tab:XgbPar}
}\end{table}

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.58\textwidth]{figures/res_width.jpg}
\caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
\label{fig:angle_reco_width}
\end{figure}

@@

\begin{figure}[!hbt]
\centering
\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
\includegraphics[width=0.48\textwidth]{figures/res_Nlayer.jpg}
}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
\includegraphics[width=0.48\textwidth]{figures/resol_Nlayer.jpg}
}
\caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$. Red histogram represents the polar angle distribution by requiring $E_{\rm{tot}}>$~10~MeV. (b) Angular resolution as a function of radiation length ($X_{0}$).}
\label{fig:angle_reco_layer}
\end{figure}

@@

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.6\textwidth]{figures/layer-event.jpg}
\caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths using the first 24 layers or the full layers. }
\label{fig:multi-parameter}
\end{figure}
